%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{fontawesome5}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}
\setlength{\footskip}{4.08003pt}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Manoj Kumar} \\ \vspace{1pt}
    \small (+91) 7042519926 $|$ \href{mailto:manojkp124@gmail.com}{\underline{manojkp124@gmail.com}} $|$ 
    \href{https://linkedin.com/in/manojku123}{\underline{linkedin.com/in/manojku123}} $|$
    \href{https://github.com/manojCode94}{\underline{github.com/manojCode94}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Netaji Subhas University of Technology West Campus (Formerly CBPGEC)}{New Delhi, Delhi}
      {Bachelor of Technology in Information Technology}{August 2011-- May 2015}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Software Engineer (SDE 1)}{September 2021 -- Present}
      {Fidelity National Information Services, Inc. (FIS Global)}{Pune, Maharashtra}
      \resumeItemListStart
        \resumeItem{Collaborated with a team of 12+ developers to develop Java RESTful API's for FIS ACBS Loan System.}
        \resumeItem{Followed Agile methodologies to patch and peer test REST APIs  using Scrum and test-driven development (TDD).}
           \resumeItem{Leveraged Azure DevOps to streamline the development and deployment process, resulting in a 30\% reduction in time-to-market.}
      \resumeItemListEnd
      
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

    \resumeSubheading
      {Associate Software Engineer}{June 2020 -- September 2021}
      {Aapna Infotech}{Gurgaon, Haryana}
      \resumeItemListStart
        \resumeItem{Assisted in the development of a full-stack Banner landing application in Spring, Hibernate/JPA, and React.}
        \resumeItem{Refactored stored procedures and optimized SQL queries, resulting in a 40\% reduction in query response time.}
        \resumeItem{Achieved an 85\% reduction in object rendering time by implementing Spring Redis caching.}
    \resumeItemListEnd

    \resumeSubheading
      {Junior Software Developer}{Februray 2019 -- March 2020}
      {Algocomputing Softwares}{Gurgaon, Haryana}
      \resumeItemListStart
        \resumeItem{Implemented an invoicing web application using Spring Boot, SQL Server, AWS and React.js as frontend.}
        \resumeItem{Wrote unit/integration tests utilizing JUnit and Mockito, resulting in a 65\% reduction in quarterly reported bugs.}
        \resumeItem{Contributed 500+ lines of code to an established codebase via Git.}
        \resumeItem{Implemented Spring Security for authentication and authorization, reducing 75\% cross site attacks in 4 weeks.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{HubConnect App: Messaging Application \href{https://github.com/manojCode94/hubconnect-app}\faGithub} $|$  \emph{Java, Spring Boot, NoSQL (Cassandra)} }{March 2023 -- Present}
          \resumeItemListStart
            \resumeItem{Developed an application that enables user to stay connected with Github friends outside platform. User can login via Github username and can send, reply, reply all and maintained the message thread in real time.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Travel map: Rate destination on Globe
          \href{https://github.com/manojCode94/travel-map}\faGithub} $|$ \emph{Node.js, Express.js, React.js, MongoDB}}{May 2023 -- Present}
          \resumeItemListStart
            \resumeItem{Built a \emph{react-map-gl} based  application that renders 3D Globe and enable users to \emph{Pin} their favorite travel destinations on the Glob. Rate, review, and share them with other users.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd

\section{Achievements}
\resumeItemListStart
    \resumeItem{
    \textbf{FIS GLobal: }Employee of the month twice for exceptional contributions in development (Aug 2022 – Dec 2022)}
     \vspace{-5pt}
    \resumeItem{Qualified for top 100 coders in FIS internal innovation competition 2022 \textbf{InnovateIN48} (World wide Hackathon)}
     \vspace{-5pt}
    \resumeItem{\textbf{LeetCode handle:} \href{https://leetcode.com/makumar/}{\underline{makumar}}}
    \vspace{-5pt}
    \resumeItem{\textbf{HackerRank handle:} \href{https://www.hackerrank.com/manojkp124}{\underline{manojKp124}}}
    \vspace{-5pt}
    \resumeItem{\textbf{Training:} Java Certified Associate (CMC LTD. (Government of India))} 
    \vspace{-5pt}
    \resumeItem{\textbf{Certification:} Data Engineering Foundation (LinkedIn)} 
    \vspace{-5pt}
\resumeItemListEnd


%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Java, JavaScript, Python, SQL(MySQL), HTML/CSS} \\
     \textbf{Frameworks}{: Spring Boot, React, Node.js, JUnit } \\
     \textbf{Developer Tools}{: Git, GitHub, Docker, AWS, Maven, Jira, VS Code, Bash, Linux} \\
     \textbf{Libraries}{: pandas, NumPy, Matplotlib}
    }}
 \end{itemize}


%-------------------------------------------
\end{document}
